---
title: "Market Volatility and Cross-Asset ETF Liquidity Commonality"
author: "Yuyao Zhang"
output: html_document
---

```{r setup, include=FALSE}
# Load packages used to display saved tables and figures in the report.
library(readr)
library(knitr)
library(here)
```

# Research Question

How does liquidity co-movement among U.S.-listed ETF proxies for different asset classes differ between high-volatility and low-volatility market conditions?

# Data and Sample

Describe the CRSP ETF data, FRED VIX data, 2010-2025 sample, ETF-day unit of observation, and PERMNO identification.

# Reproducible Workflow

Describe the numbered workflow from data collection to final outputs.

# H1 Preliminary Evidence

```{r h1-table}
# Read the H1 table created by the analysis script.
h1_table <- read_csv(
  here("output", "tables", "table2_h1_high_low_spread.csv"),
  show_col_types = FALSE
)

# Display the H1 table in the report.
kable(h1_table)
```

```{r h1-figure, out.width="90%"}
# Display the H1 boxplot created by the figure script.
knitr::include_graphics(
  here("output", "figures", "figure1_spread_boxplot.png")
)
```

# H2 Preliminary Evidence

```{r h2-table}
# Read the H2 cross-asset summary created by the analysis script.
h2_table <- read_csv(
  here("output", "tables", "table3d_h2_cross_asset_summary.csv"),
  show_col_types = FALSE
)

# Display the H2 summary table in the report.
kable(h2_table)
```

```{r h2-low, out.width="80%"}
# Display the Low-VIX correlation heatmap.
knitr::include_graphics(
  here("output", "figures", "figure2_low_vix_heatmap.png")
)
```

```{r h2-high, out.width="80%"}
# Display the High-VIX correlation heatmap.
knitr::include_graphics(
  here("output", "figures", "figure3_high_vix_heatmap.png")
)
```

# Reproducibility Reflection

Discuss licensed CRSP access, scripted cleaning, relative paths, the common-date rule, and transparent reporting.

# AI Disclosure

Describe how ChatGPT and Claude were used and how all important outputs were checked independently.
